A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-01-10 doc/large_strain.tex
first discussion on Roofline

% likwid-mpirun -np 10 -nperdomain S:10 -g MEM_DP -m $EXC
{\color{red}
Finally, we analyze the node-level performance of the two approaches using the Roofline model.
Memory bandwidth (MBytes/s) and the number of floating point operations per second (MFLOP/s) are measured using the \texttt{MEM\_DP} group of the LIKWID \cite{likwid} tool, version 4.2.1.
The measurements are done on a single socket of RRZE cluster by pinning all 10 MPI processes to this socket, whose
memory bandwidth and peak performance are $B=50 \,\rm{GB/s}$ and $P=176\, \rm{GFLOP/s}$, respectively.
[DD]TODO: plot and discuss.
}

>>>>

% likwid-mpirun -np 10 -nperdomain S:10 -g MEM_DP -m $EXC
{\color{red}
Finally, we analyze the node-level performance of the two approaches using the Roofline model.
Memory bandwidth (MBytes/s) and the number of floating point operations per second (MFLOP/s) are measured using the \texttt{MEM\_DP} group of the LIKWID \cite{likwid} tool, version 4.2.1.
The measurements are done on a single socket of RRZE cluster by pinning all 10 MPI processes to this socket, whose
memory bandwidth and peak performance are $B=50 \,\rm{GB/s}$ and $P=176\, \rm{GFLOP/s}$, respectively.
}

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.8\textwidth}
    \centering
    \includegraphics[width=\textwidth]{LIKWID_Emmy_RRZE_roofline.pdf}
    % \caption{2D multigrid mesh with 2 global refinements}
  \end{subfigure}
  \caption{Roofline model for a selection of polynomial degrees on a 2D test example.}%
  \label{fig:roofline}
\end{figure}

{\color{red}
Figure \ref{fig:roofline} shows the Roofline performance model.
As expected, the matrix-based approach is memory bound and (on average) achieves the performance of $8.5\,\rm{GFlop/s}$.
Matrix-free implementation of fine-strain elastic tangent operators (on average) leads to a much better performance of
$22.6\,\rm{GFlop/s}$, as well as about an order of magnitude higher computational intensity, but still stays in the memory bound regime.
The achieved performance is about 13\% of the peak arithmetic performance, which is considerably lower than the
70\% reported for the Laplace operation in \cite{kronbichler12}.
Further detailed studies are necessary to explain this behavior.
}
